Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-02 main.tex

A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$. We call these points the \emph{vertices} of the simplex $T$. 
If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
then we call $S$ a \textit{subsimplex} of $T$ and call $T$ a \textit{supersimplex} of $S$.

The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
and its remaining points constitute the \textit{boundary} of the simplex.

A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} if it satisfies the following conditions: 
(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
% (i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$. 
We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.} 
We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is \sout{defined as} the union 
\begin{align*}
    \underlying{\calT} := \bigcup_{ T \in \calT } T
    .
\end{align*}
We call any set triangulable if it is the underlying set of some triangulation. 
\\

@@

Whenever $\calT$ is a simplicial complex, 
the set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
% Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. In practice, we not always distinguish between points and singleton simplices. 
% Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
% \begin{remark}
    Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler1995lectures}.
% \end{remark}
}
% Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\mwl{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}

When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
Formally,
\begin{gather*}
    % \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
    \patch_{\calT}(T) := \bigcup_{ \substack{ T' \in \subsimplex_{n}(\calT) \\ T \subseteq T' } } \subsimplex(T'),
    \qquad 
    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
\end{gather*}
We also write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
A crucial structural observation is the following.~\footnote{\todo{$U_T$ looks open but it is not. With closed simplices, the patches are disjoint if they essentially disjoint.}}

@@

\subsection{...}

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
    Let $\calT$ be a face-connected $n$-dimensional finite triangulation. 
    Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$,
    and that the domain $\Omega$ is the interior of the underlying set of $\calT$. 
    Then for any $u \in W^{1,p}(\Omega)$ 
    there exists $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$ 
    and satisfying the following estimates:
    there exists an $n$-simplex $T_0 \in \calT$ with 
    \begin{gather*}
        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
    \end{gather*}
    and whenever $T_0, T_1, \dots, T_M$ is a face path,
    then for all $1 \leq m \leq$ we the following recursive estimates:
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        &
        \leq  
        \volumeratio(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(T_{\iota(m)})} 
        + 
%         C_{\PF,T_{m},F_{m},p} 
%         \left( 
%             \| \nabla u \|_{L^{p}(T_{m})} 
%             + 
%             \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
%             \| \nabla u \|_{L^{p}(T_{\iota(m)})}
%         \right)
        \left( 1 + \volumeratio(\calT)^{\frac q p} \xi(\calT)^{q} \right)^{\frac 1 q}
        C_{\PF,T_{m},F_{m},p} 
        \| \nabla u \|_{L^{p}(U_{F_m})} 
        ,
        \\
        \| w \|_{L^{p}(T_m)}
        &\leq 
        \volumeratio(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(T_{{\iota(m)}})}
        +
        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
        C_{{\PF},U_{F_m},p} 
        \| \nabla u \|_{L^{p}(U_{F_m})} 
        . 
    \end{align*}
    Here, for any $1 \leq m \leq M$, let $F_m = T_m \cap T_{m-1}$.
\end{theorem}

@@

    Now we discuss the second recursive estimate. 
    Suppose again that $1 \leq m \leq M$. 
    Recall that we write $U_{F_m} := T_m \cup T_{m-1}$. 
    We use the Poincar\'e--Friedrichs inequality over $U_{F_{m}}$,
    as given in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, 
    to find $w_{F_m} \in W^{1,p}(U_{F_m})$ such that $\nabla w_{F_m} = \nabla u$ over $U_{F_m}$ and 
    \begin{align}\label{math:wFm_inequality}
        \| w_{F_m} \|_{L^{p}(U_{F_m})} \leq C_{{\PF},U_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(U_{F_m})}.
    \end{align}
%     \cye{Since $\nabla (w_{|U_{F_m}}) = \nabla u_{F_{m}} = \nabla (u_{|U_{F_m}})$, 
    We can define the constant
    \begin{align*}
    c_{m} := w_{|U_{F_m}} - w_{F_{m}}.
    \end{align*}
    We now observe that 
    \begin{gather*}
        \| w \|_{L^{p}(T_m)}
        \leq 
        \| w_{F_m} \|_{L^{p}(T_m)}
        +
        \| c_{m} \|_{L^{p}(T_m)},
        \\
        \| c_{m} \|_{L^{p}(T_m)}
        = 
        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
        \| c_{m} \|_{L^{p}(T_{{m-1}})},
        \\ 
        \| c_{m} \|_{L^{p}(T_{{m-1}})}
        \leq 
        \| w \|_{L^{p}(T_{{m-1}})} + \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
        .
    \end{gather*}
    In combination, 
    \begin{align*}
        \| w \|_{L^{p}(T_m)}
        &
        \leq 
        \| w_{F_m} \|_{L^{p}(T_m)}
        \\&\qquad 
        +
        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
        \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}
        +
        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
        \| w \|_{L^{p}(T_{{m-1}})}
        .
    \end{align*}
    We sum the two integrals of $w_{F_m}$. 
    % 
    % 1/q = 1 - 1/p = (p-1)/p 
    When $1 < p < \infty$, recalling the complementary exponent $q = p/(p-1) \in (1,\infty)$, 
    we use H\"older's inequality to verify 
    \begin{align*}
        \| w \|_{L^{p}(T_m)}
        &\leq 
        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
        \left( 
            \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
            +
            \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
        \right)^{\frac 1 p}
        +
        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
        \| w \|_{L^{p}(T_{{m-1}})}
        \\&\leq 
        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
        \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
        +
        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
        \| w \|_{L^{p}(T_{{m-1}})}
        .
    \end{align*}
    In the special case $p=1$,
    \begin{align*}
        \| w\|_{L^{1}(T_m)}
        \leq 
        \max\left(
            1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
        \right)
        \| w_{F_m} \|_{L^{1}(U_{F_m})}
        +
        \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
        \| w \|_{L^{1}(T_{{m-1}})}
        .
    \end{align*}
    In the limit case $p=\infty$, 
    \begin{align*}
        \| w \|_{L^{\infty}(T_m)}
        \leq 
        2
        \| w_{F_m} \|_{L^{\infty}(U_{F_m})}
        +
        \| w \|_{L^{\infty}(T_{{m-1}})}
        .
    \end{align*}
    The local inequality~\eqref{math:wFm_inequality} now provides the second recursive estimate. 
    The proof is complete.
\end{proof}

\begin{corollary}
    Under the assumptions of Theorem~\ref{theorem:poincarefriedrichsestimate:grad},
    whenever $T_0, T_1, \dots, T_m$ is a face-path of $n$-simplices in $\calT$,
    we have 
    \begin{align*}
        \| w \|_{L^{p}(T_m)}
        &\leq 
        \sum_{\ell=1}^{m} 
        \volumeratio^{\frac{m-\ell}{p}}
        \min\left( 
        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
        C_{{\PF},U_{F_\ell},p} 
        ,
        \left( 1 + \volumeratio(\calT)^{\frac q p} \xi(\calT)^{q} \right)^{\frac 1 q}
        C_{\PF,T_{\ell},F_{\ell},p} 
        \right)
        \| \nabla u \|_{L^{p}(U_{F_\ell})}
        \\&
        \qquad 
        \qquad 
        +
        \volumeratio^{\frac m p}
        C_{{\PF},T_{0},p}
        \| \nabla u \|_{L^{p}(T_{0})}
        .
    \end{align*}
\end{corollary}
\begin{proof}
    This follows by repeated application of the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
\end{proof}

\begin{remark}
    The Poincar\'e--Friedrichs constant obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimates the best one as number of $n$-simplices in the triangulation $\calT$ increases. We hence target its use to local patches (stars), in particular non-convex boundary stars. The latter occur inevitably at reentrant corners. Clearly, the same building principle applies whenever we have any non-overlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $\{ U_m \}$ with a face-connected path. The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ U_m \}$. This may allow to a large decrease of the number of elements in the partition of $\overline \Omega$ and thus to a largely improved estimate of the best Poincar\'e--Friedrichs constant. 
\end{remark}

@@

Let us now turn our attention to Sobolev spaces of differential forms. 
Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, there are pointwise norms of differential $k$-forms. 
We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
such that its pointwise norm is $p$-integrable. 
The exterior derivative is defined in the sense of distributions and we introduce 
\begin{gather*}
    W^{p}\Alt^{k}(\Omega) 
    := 
    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
    .
\end{gather*}
We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
\begin{align*}
    \int_{\Omega} \cartan v \wedge u
    &=
    (-1)^{k(n-k)+1}
    \int_{\Omega} v \wedge f 
    .
\end{align*}
% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
\begin{align*}
    \int_{B_r(x)} \cartan v \wedge \tilde u
    &=
    (-1)^{k(n-k)+1}
    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
    .
\end{align*}
If that condition is satisfied, we also write 
\begin{align*}
    \trace_{\Gamma} u = 0
    .
\end{align*}
Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
Lastly, we introduce the closed subspaces 
\begin{gather*}
    W^{p}_{0}\Alt^{k}(\Omega) 
    := 
    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
    .
\end{gather*}
% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
\mwl{This is a closed subspace. We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$.}

@@

The discussion for the Bogovski\u{\i} operator is almost analogous. 

@@

@@

    u(x)

>>>>

A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$. We call these points the \emph{vertices} of the simplex $T$. 
The strictly positive convex combinations of the vertices of the simplex constitute the \textit{ interior} of the simplex,
and its remaining points constitute the \textit{boundary} of the simplex.
If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
then we call $S$ a \textit{subsimplex} of $T$ and call $T$ a \textit{supersimplex} of $S$.

A finite family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation} if it satisfies the following conditions: 
(i) $\calT$ contains all the subsimplices of its members (ii) any non-empty intersection of two members of $\calT$ is a common subsimplex of each of them. 
We say that a simplicial complex $\calT$ has \textit{dimension $n$} or is \textit{$n$-dimensional} if each of its simplices is a subset of an $n$-dimensional member of that triangulation.\footnote{Simplicial complexes that we call $n$-dimensional are called purely $n$-dimensional in the literature on polytopes~(cf.\ \cite{ziegler1995lectures}) \cye{and simply ``simplicial meshes'' in the finite element literature}.} 
We also write $\underlying{\calT}$ for the \textit{underlying set} of the simplicial complex $\calT$, which is the union 
\begin{align*}
    \underlying{\calT} := \bigcup_{ T \in \calT } T
    .
\end{align*}
We call any set triangulable if it is the underlying set of some triangulation. 
\\

@@

Whenever $\calT$ is a simplicial complex, 
the set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
% Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. In practice, we not always distinguish between points and singleton simplices. 
% Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
    Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler1995lectures}.
}
% Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\mwl{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}

When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
Formally,
\begin{gather*}
    % \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
    \patch_{\calT}(T) := \bigcup_{ \substack{ T' \in \subsimplex_{n}(\calT) \\ T \subseteq T' } } \subsimplex(T'),
    \qquad 
    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
\end{gather*}
We also write $\Minako_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
A crucial structural observation is the following.

@@

\subsection{Shape measures and related quantities}

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
    Let $\calT$ be a face-connected $n$-dimensional finite triangulation. 
    Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$,
    and that the domain $\Omega$ is the interior of the underlying set of $\calT$. 
    Then for any $u \in W^{1,p}(\Omega)$ 
    there exists $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$ 
    and satisfying the following estimates:
    there exists an $n$-simplex $T_0 \in \calT$ with 
    \begin{gather*}
        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
    \end{gather*}
    and whenever $T_0, T_1, \dots, T_M$ is a face path,
    then for all $1 \leq m \leq$ we the following recursive estimates:
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        &
        \leq  
        \volumeratio(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(T_{\iota(m)})} 
        + 
%         C_{\PF,T_{m},F_{m},p} 
%         \left( 
%             \| \nabla u \|_{L^{p}(T_{m})} 
%             + 
%             \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
%             \| \nabla u \|_{L^{p}(T_{\iota(m)})}
%         \right)
        \left( 1 + \volumeratio(\calT)^{\frac q p} \xi(\calT)^{q} \right)^{\frac 1 q}
        C_{\PF,T_{m},F_{m},p} 
        \| \nabla u \|_{L^{p}(\Minako_{F_m})} 
        ,
        \\
        \| w \|_{L^{p}(T_m)}
        &\leq 
        \volumeratio(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(T_{{\iota(m)}})}
        +
        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
        C_{{\PF},\Minako_{F_m},p} 
        \| \nabla u \|_{L^{p}(\Minako_{F_m})} 
        . 
    \end{align*}
    Here, for any $1 \leq m \leq M$, let $F_m = T_m \cap T_{m-1}$.
\end{theorem}

@@

    Now we discuss the second recursive estimate. 
    Suppose again that $1 \leq m \leq M$. 
    Recall that we write $\Minako_{F_m} := T_m \cup T_{m-1}$. 
    We use the Poincar\'e--Friedrichs inequality over $\Minako_{F_{m}}$,
    as given in Lemma~\ref{lemma:poincarefriedrichsoverfacepatch}, 
    to find $w_{F_m} \in W^{1,p}(\Minako_{F_m})$ such that $\nabla w_{F_m} = \nabla u$ over $\Minako_{F_m}$ and 
    \begin{align}\label{math:wFm_inequality}
        \| w_{F_m} \|_{L^{p}(\Minako_{F_m})} \leq C_{{\PF},\Minako_{F_m},p} \| \nabla w_{F_m} \|_{L^{p}(\Minako_{F_m})}.
    \end{align}
%     \cye{Since $\nabla (w_{|\Minako_{F_m}}) = \nabla u_{F_{m}} = \nabla (u_{|\Minako_{F_m}})$, 
    We can define the constant
    \begin{align*}
    c_{m} := w_{|\Minako_{F_m}} - w_{F_{m}}.
    \end{align*}
    We now observe that 
    \begin{gather*}
        \| w \|_{L^{p}(T_m)}
        \leq 
        \| w_{F_m} \|_{L^{p}(T_m)}
        +
        \| c_{m} \|_{L^{p}(T_m)},
        \\
        \| c_{m} \|_{L^{p}(T_m)}
        = 
        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
        \| c_{m} \|_{L^{p}(T_{{m-1}})},
        \\ 
        \| c_{m} \|_{L^{p}(T_{{m-1}})}
        \leq 
        \| w \|_{L^{p}(T_{{m-1}})} + \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
        .
    \end{gather*}
    In combination, 
    \begin{align*}
        \| w \|_{L^{p}(T_m)}
        &
        \leq 
        \| w_{F_m} \|_{L^{p}(T_m)}
        \\&\qquad 
        +
        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
        \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}
        +
        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
        \| w \|_{L^{p}(T_{{m-1}})}
        .
    \end{align*}
    We sum the two integrals of $w_{F_m}$. 
    % 
    % 1/q = 1 - 1/p = (p-1)/p 
    When $1 < p < \infty$, recalling the complementary exponent $q = p/(p-1) \in (1,\infty)$, 
    we use H\"older's inequality to verify 
    \begin{align*}
        \| w \|_{L^{p}(T_m)}
        &\leq 
        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
        \left( 
            \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
            +
            \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
        \right)^{\frac 1 p}
        +
        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
        \| w \|_{L^{p}(T_{{m-1}})}
        \\&\leq 
        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
        \| w_{F_{m}} \|_{L^{p}(\Minako_{F_m})} 
        +
        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
        \| w \|_{L^{p}(T_{{m-1}})}
        .
    \end{align*}
    In the special case $p=1$,
    \begin{align*}
        \| w\|_{L^{1}(T_m)}
        \leq 
        \max\left(
            1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
        \right)
        \| w_{F_m} \|_{L^{1}(\Minako_{F_m})}
        +
        \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
        \| w \|_{L^{1}(T_{{m-1}})}
        .
    \end{align*}
    In the limit case $p=\infty$, 
    \begin{align*}
        \| w \|_{L^{\infty}(T_m)}
        \leq 
        2
        \| w_{F_m} \|_{L^{\infty}(\Minako_{F_m})}
        +
        \| w \|_{L^{\infty}(T_{{m-1}})}
        .
    \end{align*}
    The local inequality~\eqref{math:wFm_inequality} now provides the second recursive estimate. 
    The proof is complete.
\end{proof}

\begin{corollary}
    Under the assumptions of Theorem~\ref{theorem:poincarefriedrichsestimate:grad},
    whenever $T_0, T_1, \dots, T_m$ is a face-path of $n$-simplices in $\calT$,
    we have 
    \begin{align*}
        \| w \|_{L^{p}(T_m)}
        &\leq 
        \sum_{\ell=1}^{m} 
        \volumeratio^{\frac{m-\ell}{p}}
        \min\left( 
        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
        C_{{\PF},\Minako_{F_\ell},p} 
        ,
        \left( 1 + \volumeratio(\calT)^{\frac q p} \xi(\calT)^{q} \right)^{\frac 1 q}
        C_{\PF,T_{\ell},F_{\ell},p} 
        \right)
        \| \nabla u \|_{L^{p}(\Minako_{F_\ell})}
        \\&
        \qquad 
        \qquad 
        +
        \volumeratio^{\frac m p}
        C_{{\PF},T_{0},p}
        \| \nabla u \|_{L^{p}(T_{0})}
        .
    \end{align*}
\end{corollary}
\begin{proof}
    This follows by repeated application of the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
\end{proof}

\begin{remark}
    The Poincar\'e--Friedrichs constant obtained from Theorem~\ref{theorem:poincarefriedrichsestimate:grad} increasingly overestimates the best one as number of $n$-simplices in the triangulation $\calT$ increases. We hence target its use to local patches (stars), in particular non-convex boundary stars. The latter occur inevitably at reentrant corners. Clearly, the same building principle applies whenever we have any non-overlapping partition of $\overline \Omega$ into convex local patches of $n$-simplices $\{ \Minako_m \}$ with a face-connected path. The proof proceeds verbatim, where we merely replace the simplices $\{ T_{m} \}$ by the convex local patches $\{ \Minako_m \}$. This may allow to a large decrease of the number of elements in the partition of $\overline \Omega$ and thus to a largely improved estimate of the best Poincar\'e--Friedrichs constant. 
\end{remark}

@@

Let us now turn our attention to Sobolev spaces of differential forms. 
Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, there are pointwise norms of differential $k$-forms. 
We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
such that its pointwise norm is $p$-integrable. 
The exterior derivative is defined in the sense of distributions and we introduce 
\begin{gather*}
    W^{p}\Alt^{k}(\Omega) 
    := 
    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
    .
\end{gather*}
We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
\begin{align*}
    \int_{\Omega} \cartan v \wedge u
    &=
    (-1)^{k(n-k)+1}
    \int_{\Omega} v \wedge f 
    .
\end{align*}
% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
% such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\bbR^{n})$ 
whose support lies in the open ball $B_r(x)$
we have the integration by parts formula
\begin{align*}
    \int_{B_r(x)} \cartan v \wedge \tilde u
    &=
    (-1)^{k(n-k)+1}
    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
    .
\end{align*}
If that condition is satisfied, we also write 
\begin{align*}
    \trace_{\Gamma} u = 0
    .
\end{align*}
Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
Lastly, we introduce the closed subspaces 
\begin{gather*}
    W^{p}_{0}\Alt^{k}(\Omega) 
    := 
    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
    .
\end{gather*}
% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
This is a closed subspace. We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$. We also observe that $W^{p}\Alt^{n}(\Omega) = W^{p}_{0}\Alt^{n}(\Omega)$.

@@

The discussion for the Bogovski\u{\i} operator is analogous. 

@@

    \int_{1}^{\infty} 

@@

    -u(x)
